---
title: "Publilia-03-survivorship.Rmd"
author: "micah fletcher"
date: "8/4/2023"
output: html_document
---

# Required libraries and functions
```{r}
library(tidyverse)
library(lubridate)
library(ggpubr)
library(ggh4x)
library(rstatix)
library(emmeans)
library(effectsize)
library(gt)
library(gtsummary)
theme_gtsummary_compact()
library(flextable)
library(multcompView)
library(here)
library(bbmle)

source(here("R/custom_functions.R"))
```

# 0 - Data import

## Data for regressions
```{r}
surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
```

# 1 - Model fitting and plotting figures

## Main -`desL * ants_treatment * desL^2`

### Fit models
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ant_treatment")

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

models_output <- list(
  hatch = des_hatch.desL.ant_treatment.quad$fits,
  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
  Esurv = des_Esurv.desL.ant_treatment.quad$fits
)
```

### Plot figures
```{r}
(desL.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad$p +
                 theme(legend.position = c(0.8,0.95)) + 
                 ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desL.ant_treatment.quad.final.png"),
       desL.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```


### Print model outputs
#### Hatch
```{r}
print_glm_stats(models_output$hatch)
```

#### Nsurv
```{r}
print_glm_stats(models_output$Nsurv)
```

#### Esurv
```{r}
print_glm_stats(models_output$Esurv)
```

### Tables

#### Sample sizes
```{r}
(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
  mutate(ants = ant_treatment,
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desL.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desL.ant_treatment.docx"))
```

#### Parameter fit tables
```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desL.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ant_treatment.quad.qb.tbl, 
                Nsurv.desL.ant_treatment.quad.qb.tbl, 
                Esurv.desL.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desL.ants_treatment.quad.docx"))
```


## Supp 1 - `desL * ants_gt2 * desL^2`

### Fit models
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="des", treatment="ants_gt2d")

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ants_gt2d")

# egg survivorship
des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ants_gt2d")
```

### Plot figures
```{r}
(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desL.ants_gt2d.quad.final.png"),
       desL.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

### Tables

#### Sample sizes
```{r}
(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desL.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desL.ants_gt2d.docx"))
```

#### Parameter fit tables
```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desL.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ants_gt2d.quad.qb.tbl, 
                Nsurv.desL.ants_gt2d.quad.qb.tbl, 
                Esurv.desL.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desL.ants_gt2d.quad.docx"))
```

## Supp 2 -`desP * ants_gt2 * desP^2`

### Fit models
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="desP", treatment="ants_gt2d")

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="desP", treatment="ants_gt2d")

# egg survivorship
des_Esurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="desP", treatment="ants_gt2d")
```

### Plot figures
```{r}
(desP.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desP.ants_gt2d.quad.final.png"),
       desP.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

### Tables

#### Sample sizes
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desP.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desP.ants_gt2d.docx"))
```

#### Parameter fits table
```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desP.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desP.ants_gt2d.quad.qb.tbl, 
                Nsurv.desP.ants_gt2d.quad.qb.tbl, 
                Esurv.desP.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desP.ants_gt2d.quad.docx"))
```

## Supp 3 -`desP * ant_s_gt2_treatment * desP^2`

### Fit models
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="desP", treatment="ant_treatment")

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="desP", treatment="ant_treatment")

# egg survivorship
des_Esurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="desP", treatment="ant_treatment")
```

### Plot figures
```{r}
(desP.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ant_treatment.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desP.ant_treatment.quad.final.png"),
       desP.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

### Tables

#### Sample sizes
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ant_treatment <- surv_reg_data %>%
  mutate(ants = ifelse(ant_treatment==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desP.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desP.ant_treatment.docx"))
```

#### Parameter fit tables
```{r}
hatch.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desP.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desP.ant_treatment.quad.qb.tbl, 
                Nsurv.desP.ant_treatment.quad.qb.tbl, 
                Esurv.desP.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desP.ant_treatment.quad.docx"))
```

# 2 - qAICc across all models
```{r}
# qAICc into separate tables
# qaicc
(qAICc_gt_tbl_hatch_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Hatching success",4)),
  qAICc = c(
    get_qaicc(des_hatch.desL.ant_treatment.quad$fits),
    get_qaicc(des_hatch.desP.ant_treatment.quad$fits),
    get_qaicc(des_hatch.desL.ants_gt2d.quad$fits),
    get_qaicc(des_hatch.desP.ants_gt2d.quad$fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Nsurv_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Nymph survivorship",4)),
  qAICc = c(
    get_qaicc(des_Nsurv.desL.ant_treatment.quad$fits),
    get_qaicc(des_Nsurv.desP.ant_treatment.quad$fits),
    get_qaicc(des_Nsurv.desL.ants_gt2d.quad$fits),
    get_qaicc(des_Nsurv.desP.ants_gt2d.quad$fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Esurv_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Egg survivorship",4)),
  qAICc = c(
    get_qaicc(des_Esurv.desL.ant_treatment.quad$fits),
    get_qaicc(des_Esurv.desP.ant_treatment.quad$fits),
    get_qaicc(des_Esurv.desL.ants_gt2d.quad$fits),
    get_qaicc(des_Esurv.desP.ants_gt2d.quad$fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))
```

# 3 - Stats interpretation
```{r}
## Hatch
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_hatch.desL.ant_treatment.quad$fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_hatch.desL.ant_treatment.quad$fits$mai.qb)

# Nsurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)

# Esurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Esurv.desL.ant_treatment.quad$fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Esurv.desL.ant_treatment.quad$fits$mai.qb)
```
